Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
update
new

\author{Joshua Lande,\\
Stefan Funk,\\
Markus Ackermann}
\date{August 25, 2011}

@@

  \includegraphics[scale=0.45]{plots/title.png}

  \begin{itemize}
    \item Cat II paper
    \item Target Journal: ApJ
    \item Pub Board: \url{https://www-glast.stanford.edu/cgi-prot/pub_download?id=662}
    \item Internal referees: Marianne Lemoine-Goumard + Johann Cohen-Tanugi (+ unofficially Jean Ballet)
      \begin{itemize}
        \item Thanks for all your help!
      \end{itemize}
    \item Ready for submission
  \end{itemize}
\end{frame}

@@

\begin{frame}{Fig. 3+4: False-Detection Rate}
  \begin{columns}
    \column{.5\textwidth} 
    \includegraphics[scale=0.4]{plots/ts_ext_emin_1000_color.pdf}
    \column{.5\textwidth} 
    \begin{itemize}
      \item Simulate point-like sources
      \item Test for extension
      \item Good agreement with Wilk's Theorem
      \item Use $\sqrt{\mathrm{TS}_\mathrm{ext}}$
        as a measure of significance
      \item $\sim 20,000$ Simulations per spectral model!
      \item Test in 1 GeV to 100 GeV + 10 GeV to 100 GeV
        energy range
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 5+6+7: Detection Threshold}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Detetion threshold to extension
      \item $\langle\text{TS}_\text{ext}\rangle=16$
      \item Vary spectra, background, energy range
      \item Overlay extended sources
      \item Reference for future publications!
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 8+9: Effects of Source Confusion}
  Non-nested model comparison
  \begin{equation*}
    \text{TS}_\text{2pts} = 2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
  \end{equation*}

  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.30]{plots/confusion_2pts_plot_color.pdf}

    Simulate extended sources. Fit as point-like sources.

    \column{.4\textwidth}
    \includegraphics[scale=0.30]{plots/confusion_extended_plot_color.pdf}

    Simulate point-like sources. Fit for extension.
  \end{columns}
\end{frame}

@@

@@

>>>>

\author{Joshua Lande,\\
Stefan Funk,\\
Markus Ackermann}
\date{February 15, 2012}

@@

  \includegraphics[scale=0.65]{plots/title.pdf}

  \begin{itemize}
    \item Cat II paper
    \item Internal referees: Marianne Lemoine-Goumard + Johann Cohen-Tanugi (+ unofficially Jean Ballet)
    \item Submitted to ApJ
  \end{itemize}
\end{frame}

@@

\begin{frame}{Fig. 2: LAT PSF}
    \includegraphics[scale=0.5]{plots/compare_disk_gauss_color.pdf}
\end{frame}

\begin{frame}{Table 1: False-Detection Rate}
  \begin{columns}
    \column{.5\textwidth} 
    \includegraphics[scale=0.35]{plots/table_1.pdf}
    \column{.5\textwidth} 
    \begin{itemize}
      \item Simulate point-like sources
      \item Test for extension
      \item Good agreement with Wilk's Theorem
      \item Use $\sqrt{\mathrm{TS}_\mathrm{ext}}$
        as a measure of significance
      \item $\sim 20,000$ Simulations per spectral model!
      \item Test in 1 GeV to 100 GeV + 10 GeV to 100 GeV
        energy range
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 3+4: False-Detection Rate (cont)}
  \begin{columns}
    \column{.5\textwidth} 
    \includegraphics[scale=0.35]{plots/ts_ext_emin_1000_color.pdf}
    \column{.5\textwidth} 
    \includegraphics[scale=0.35]{plots/ts_ext_emin_10000_color.pdf}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 5: Detection Threshold}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.5]{plots/index_sensitivity_color.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Detetion threshold to extension
      \item $\langle\text{TS}_\text{ext}\rangle=16$
      \item Vary spectra, background, energy range
      \item Overlay extended sources
      \item Reference for future publications!
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 6: Detection Threshold (cont)}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.5]{plots/all_sensitivity_color.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Compute sensitivty for different background levels, energy ranges.
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 7: Detection Threshold (cont)}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.5]{plots/time_sensitivity_color.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Compute sensitivty after 10 years.
    \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 8: Effects of Source Confusion}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.50]{plots/confusion_extended_plot_color.pdf}
    \column{.4\textwidth}
    \begin{enumerate}
      \item Non-nested model comparison
        \begin{multline*}
          \text{TS}_\text{2pts} =  \\
          2 \log(\mathcal{L}_\text{2pts}/\mathcal{L}_\text{ps})
        \end{multline*}
      \item Simulate extended sources. 
      \item Fit as point-like sources.
    \end{enumerate}
  \end{columns}
\end{frame}

\begin{frame}{Fig. 9: Effects of Source Confusion (cont)}

  \begin{columns}

    \column{.6\textwidth}
    \includegraphics[scale=0.50]{plots/confusion_2pts_plot_color.pdf}
    \column{.4\textwidth}
    \begin{enumerate}
      \item Simulate point-like sources. 
      \item Fit for extension.
    \end{enumerate}
  \end{columns}
\end{frame}

@@

\begin{frame}{Fig. 1: IC~443}
    \includegraphics[scale=0.5]{plots/four_plots_ic443_color.pdf}
\end{frame}

\begin{frame}{Fig. 11: Residual TS Map}
  \includegraphics[scale=0.5]{plots/res_tsmap_ic443_color.pdf}
\end{frame}

@@

\begin{frame}{Fig. 12: Systematics in the plane}
  \includegraphics[scale=0.5]{plots/example_bad_fit_color.pdf}
\end{frame}
